The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-11 article.tex
changes to intro

Mobile robot security is a rapidly developing area of interest in robotics. As mobile robotic systems become more ubiquitous, the need for security and reliability continues to grow. One avenue for advancement in this is distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this is a state detection system validation allows agents to detect compromised agents in their environment. The detection of such compromised agents can be used to create a \textit{trusted set} within a group, providing a multi-node trust system. A TurtleBot running Robot Operating System (ROS) platform is used for implementation and performance is also evaluated in the Gazebo simulator.

@@

\section{Introduction}
With drones in land, air and sea coming into the growing consumer and private markets, the security involved in groups of these machines must be studied further. Robot security has landed headlines across a variety of commonly used devices, car hacking having a prominent impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al, posing many questions about the protocol used in vehicles \cite{greenberg2015hackers}. As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes are based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.

>>>>

Mobile robot security is a rapidly developing area of interest in robotics. As interconnected mobile robotic systems become more ubiquitous, the need for security and reliability continues to grow. One avenue for advancement in this is distributed systems coordinated between multiple agents. This paper proposes a state detection system validation which allows agents to detect compromised agents in their environment. Security is retained by means of a distributed state estimation system that uses Kalman filters and a secure ad-hoc channel to manage communications between the agents. The detection of such compromised agents can be used to create a \textit{trusted set} within a group, providing a multi-node trust system. A TurtleBot running Robot Operating System (ROS) platform is used for implementation and performance is also evaluated in the Gazebo simulator.

@@

\section{Introduction}
Robot security has landed headlines across a variety of commonly used networked devices, car hacking being a prominent example of a security flaw that could have catastrophic impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al, posing many questions about the protocol used in vehicles and how other cars in the same network can work to detect and isolate a compromised agent \cite{greenberg2015hackers}.

This network of agents is what is commonly referred to as a distributed system; a network of agents working to achieve a common goal. Among distributed systems come in a combination of centralized and decentralized characteristics, the two main extremes a system can be categorized as. Centralized systems have the advantage of control at the expense of one central point of failure, whereas a well structured decentralized system can be resilient to various attacks.

As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes are based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.
